### 2023-01-29 README.rmd
removing the package raster and rgdal from dependencies
updating the readme

Here we are! We are moving from `maptools`, `sp` and `rgeos` to `sf` and `tmap`. All the functions and the documentation were modified accordingly. If you spot an error or a bug, please open an issue on github.

@@

@@

`geocmeans` version 0.1.0 is licensed under [GPL2 License](https://github.com/JeremyGelb/geocmeans/blob/master/LICENSE.txt).

>>>>

Here we are! We are moving from `maptools`, `sp`, `rgeos`, `raster` and `rgdal` to `sf`, `terra` and `tmap`. All the functions and the documentation were modified accordingly. If you spot an error or a bug, please open an issue on github.

@@

For each algorithm, it is possible to calculate a "robust version" and to add a noise group (used to catch outliers). See the parameters `robust` and `noise_cluser` in the documentation for more details.

@@

`geocmeans` version 0.3.2 is licensed under [GPL2 License](https://github.com/JeremyGelb/geocmeans/blob/master/LICENSE.txt).
